### 2014-11-01 implementation.tex
implementation spell-check

The shim layer maintains a causally consistent in-memory snapshot of a subset
of objects in the backing store, by explicitly tracking dependencies introduced
between effects due to visibility, session and same transaction relations.
Dependence tracking is similar to the techniques presented in~\cite{BoltOn}
and~\cite{Eiger}. Because Cassandra provides durability, convergence and fault
tolerance, each shim layer node simply acts as a soft-state cache, do not
commicate directly with each other, and can safely be terminated at any point.
Similarly, new shim layer nodes can be spawned on demand.

The shim layer nodes periodically fetch updates from the store for eventually
consistent operations, and on-demand for causally consistent and stronly
consistent operations. Strongly consistent operations are performed after
obtaining exclusive leases on objects. The lease mechanism is implemented with
the help of Cassandra's support for conditional updates and expiring columns.

@@

Performing summarization in the backing store is more complicated; the whole
process needs to be atomic from a clients perspective, but Cassadra does not
provide multirow transactions. We have implemented a highly available
implementation of summarization that permits concurrent client operations, but
nonetheless prohibits these operations from witnessing intermediate states of
the summarization process.

>>>>

The shim layer maintains a causally consistent in-memory snapshot of a subset
of objects in the backing store, by explicitly tracking dependencies introduced
between effects due to visibility, session and same transaction relations.
Dependence tracking is similar to the techniques presented in~\cite{BoltOn}
and~\cite{Eiger}. Because Cassandra provides durability, convergence and fault
tolerance, each shim layer node simply acts as a soft-state cache, do not
communicate directly with each other, and can safely be terminated at any point.
Similarly, new shim layer nodes can be spawned on demand.

The shim layer nodes periodically fetch updates from the store for eventually
consistent operations, and on-demand for causally consistent and strongly
consistent operations. Strongly consistent operations are performed after
obtaining exclusive leases on objects. The lease mechanism is implemented with
the help of Cassandra's support for conditional updates and expiring columns.

@@

Performing summarization in the backing store is more complicated; the whole
process needs to be atomic from a clients perspective, but Cassandra does not
provide multi-row transactions. We have implemented a highly available
implementation of summarization that permits concurrent client operations, but
nonetheless prohibits these operations from witnessing intermediate states of
the summarization process.
